Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2018-10-06 paper/paper.tex
added O'Neal 2018 reference

However, existing techniques are inadequate to determine how viral genetic diversity contributes to cell-to-cell heterogeneity during infection.
Flow cytometry and fluorescent reporters only measure protein levels~\citep{brooke2013most, guo2017single}, and current single-cell transcriptomic techniques primarily measure abundance of transcripts and provide only fragmentary information on their sequences~\citep{russell2018extreme, zanini2018single, zanini2018virus, steuerman2018dissection, saikia2018simultaneous}.
None of these techniques reliably reveal if the virion infecting a specific cell has some idiosyncratic mutation, despite the fact that such mutations are common even if cells are infected with a nominally ``wild-type'' stock of virus.

@@

\section{Discussion}
We have determined the full sequences of all viral genes expressed in single influenza-infected cells, and examined how viral mutations and gene-expression defects associate with infection outcome in each cell.
Methodologically, our major advance is to measure the \emph{genotypes} of viruses in addition to the abundance of viral components (i.e., transcripts, proteins, or progeny virions) as has been done by prior single-cell studies~\citep{russell2018extreme, zanini2018single, zanini2018virus, steuerman2018dissection, saikia2018simultaneous, zhu2009growth, schulte2014single, akpinar2016high, heldt2015single, brooke2013most}.
Our method builds on the observation by \citet{saikia2018simultaneous} and \citet{zanini2018virus} that fragmentary viral genetic information can be obtained by more standard single-cell transcriptomic techniques.
To make this information complete, we have coupled single-cell transcriptomics with long-read PacBio sequencing of viral genes, a strategy analogous to that used by \cite{gupta2018single} to obtain full-length isoforms of some cellular genes in single cells.

>>>>

However, existing techniques are inadequate to determine how viral genetic diversity contributes to cell-to-cell heterogeneity during infection.
Flow cytometry and fluorescent reporters only measure protein levels~\citep{brooke2013most, guo2017single}, and current single-cell transcriptomic techniques primarily measure abundance of transcripts and provide only fragmentary information on their sequences~\citep{russell2018extreme, zanini2018single, zanini2018virus, steuerman2018dissection, saikia2018simultaneous, oneal2018west}.
None of these techniques reliably reveal if the virion infecting a specific cell has some idiosyncratic mutation, despite the fact that such mutations are common even if cells are infected with a nominally ``wild-type'' stock of virus.

@@

\section{Discussion}
We have determined the full sequences of all viral genes expressed in single influenza-infected cells, and examined how viral mutations and gene-expression defects associate with infection outcome in each cell.
Methodologically, our major advance is to measure the \emph{genotypes} of viruses in addition to the abundance of viral components (i.e., transcripts, proteins, or progeny virions) as has been done by prior single-cell studies~\citep{russell2018extreme, zanini2018single, zanini2018virus, steuerman2018dissection, saikia2018simultaneous, oneal2018west, zhu2009growth, schulte2014single, akpinar2016high, heldt2015single, brooke2013most}.
Our method builds on the observation by \citet{saikia2018simultaneous} and \citet{zanini2018virus} that fragmentary viral genetic information can be obtained by more standard single-cell transcriptomic techniques.
To make this information complete, we have coupled single-cell transcriptomics with long-read PacBio sequencing of viral genes, a strategy analogous to that used by \cite{gupta2018single} to obtain full-length isoforms of some cellular genes in single cells.
